|

### 2020-08-25 pre-analysis-plan/freire-skarbek-lynching.Rmd
acknowledgement order

[^thanks]: We thank Louise Araújo, Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.

>>>>

[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
